% To compile, use: latexmk -pvc -lualatex dissertation -latexoption="--shell-escape"
%\documentclass[draft,12pt]{nddiss2e}
% \documentclass[final,12pt]{nddiss2e}
\documentclass[noinfo,final,nonatbib]{nddiss2e}
% \usepackage{showframe}
\usepackage{mdframed}
\usepackage{colortbl}
\usepackage{amssymb}
\usepackage{afterpage}
\usepackage{bigdelim}
\usepackage{listings}
\usepackage{makecell}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{newunicodechar}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{physics}
\usepackage{polyglossia}
\usepackage{minted}
\surroundwithmdframed[linewidth=2pt]{minted}
\usepackage[
  type={CC},
  modifier={by-sa},
  version={4.0},
]{doclicense}

\let\abs\relax
\usepackage{siunitx}

\usepackage[noabbrev,nameinlink,capitalize]{cleveref}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup[subfigure]{subrefformat=simple,labelformat=simple}
    \renewcommand\thesubfigure{(\alph{subfigure})}

\usepackage[flushleft]{threeparttablex}
\usepackage{tikz}
\usepackage[compat=1.1.0]{tikz-feynman}
\usepackage{tabulary}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcolumntype{K}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{Z}{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}X}
\usepackage{xpatch}
\usepackage[subtle]{savetrees}
\AtBeginDocument{\thinmuskip = 3mu}

\usepackage[disable]{todonotes}
\usepackage{accents}
\usepackage{csquotes}
\usepackage{unicode-math}

\lstset{
  basicstyle=\ttfamily,
}

\sisetup{
  range-phrase=--,
  range-units=single,
  group-minimum-digits=4,
  multi-part-units=single,
  separate-uncertainty,
	table-number-alignment=center,
}
\interfootnotelinepenalty=10000
\usetikzlibrary{arrows,calc,fit,positioning,shapes}

\usepackage{mathtools}
\usepackage{autonum} % only number labeled equations
\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}

\overfullrule=0pt
\usepackage[giveninits=true,isbn=false,sorting=none]{biblatex}

\AtEveryBibitem{%
  \clearlist{language}%
  \ifentrytype{book}{\clearfield{url}}{}%
  \clearlist{abstract}%
  \clearfield{eprintclass}%
  \clearfield{note}
}
\DeclareFieldFormat{labelnumberwidth}{#1\adddot}
% \DeclareFieldFormat{url}{\printtext{URL}\space\href{#1}{\nolinkurl{#1}}}
% \DeclareFieldFormat{doi}{\printtext{DOI}\addcolon\space\href{http://dx.doi.org/#1}{\nolinkurl{#1}}}
\DeclareFieldFormat{shorturl}{\nolinkurl{#1}}
\DeclareFieldFormat{url}{%
  \href{#1}{\printfield{shorturl}}}
\DeclareFieldFormat{doi}{\href{http://dx.doi.org/#1}{\nolinkurl{doi:#1}}}
\DeclareFieldFormat{eprint:arxiv}{%
  \ifhyperref
    {\href{http://arxiv.org/abs/#1}{%
       \nolinkurl{arxiv:#1}%
       \iffieldundef{eprintclass}
         {}
         {\addspace\texttt{\mkbibbrackets{\thefield{eprintclass}}}}}}
    {\nolinkurl{arxiv:#1}
     \iffieldundef{eprintclass}
       {}
       {\addspace\texttt{\mkbibbrackets{\thefield{eprintclass}}}}}}
\setcounter{biburllcpenalty}{9000}
\setcounter{biburlucpenalty}{9000}
\setcounter{biburlnumpenalty}{9000}
\setlength\bibitemsep{\baselineskip}

\renewbibmacro*{in:}{%
  \printtext{%
    \bibstring{In}\intitlepunct}}
\renewbibmacro*{doi+eprint+url}{%
  \iftoggle{bbx:url}
    {\iffieldundef{doi}{\usebibmacro{url+urldate}}{}}
    {}%
  \newunit\newblock
  \iftoggle{bbx:eprint}
    {\iffieldundef{doi}{\usebibmacro{eprint}}{}}
    {}%
  \newunit\newblock
  \iftoggle{bbx:doi}
    {\printfield{doi}}
    {}}

\addbibresource{dissertation.bib}

% Remove the abstract.
\DeclareSourcemap{
  \maps[datatype=bibtex]{
    \map[overwrite=true]{
      \step[fieldset=abstract, null]
    }
    \map[overwrite=true]{
      \step[fieldsource=url]
      \step[fieldset=shorturl, origfieldval]
      \step[fieldsource=shorturl, match=\regexp{https?://}, replace={}]
    }
  }
}

\DeclareDocumentCommand\Pe{}{\ensuremath{e}\xspace}
\DeclareDocumentCommand\Pp{}{\ensuremath{\text{p}}\xspace}
\DeclareDocumentCommand\Pg{}{\ensuremath{\text{g}}\xspace}
\DeclareDocumentCommand\Pnu{}{\ensuremath{\nu}\xspace}
\DeclareDocumentCommand\Pmu{}{\ensuremath{\mu}\xspace}
\DeclareDocumentCommand\Ptau{}{\ensuremath{\tau}\xspace}
\DeclareDocumentCommand\Ptop{}{\ensuremath{\text{t}}\xspace}
\DeclareDocumentCommand\Ptopbar{}{\ensuremath{\bar{\text{t}}}\xspace}
\DeclareDocumentCommand\Ppi{}{\ensuremath{\pi}\xspace}
\DeclareDocumentCommand\Pb{}{\ensuremath{\text{b}}\xspace}
\DeclareDocumentCommand\Pd{}{\ensuremath{\text{d}}\xspace}
\DeclareDocumentCommand\Pc{}{\ensuremath{\text{c}}\xspace}
\DeclareDocumentCommand\Ps{}{\ensuremath{\text{s}}\xspace}
\DeclareDocumentCommand\Pu{}{\ensuremath{\text{u}}\xspace}
\DeclareDocumentCommand\PW{}{\ensuremath{\text{W}}\xspace}
\DeclareDocumentCommand\PH{}{\ensuremath{\text{H}}\xspace}
\DeclareDocumentCommand\PZ{}{\ensuremath{\text{Z}}\xspace}
\DeclareDocumentCommand\Phad{}{\ensuremath{h}\xspace}
\DeclareDocumentCommand\Ptauh{}{\Ptau_\Phad\xspace}
\DeclareDocumentCommand\Pkaon{}{\ensuremath{K}\xspace}
\DeclareDocumentCommand\Pb{}{\ensuremath{\text{b}}\xspace}
\DeclareDocumentCommand\Pq{}{\ensuremath{\text{q}}\xspace}
\DeclareDocumentCommand\Pqbar{}{\ensuremath{\bar{\text{q}}}\xspace}
\DeclareDocumentCommand\Pbbar{}{\ensuremath{\bar{\text{b}}}\xspace}
\DeclareDocumentCommand\lep{}{\ensuremath{{\ell}}\xspace}
\DeclareDocumentCommand\ttH{}{\ensuremath{\Ptop\bar{\Ptop}\PH}\xspace}
\DeclareDocumentCommand\ttZ{}{\ensuremath{\Ptop\bar{\Ptop}\PZ}\xspace}
\DeclareDocumentCommand\ttW{}{\ensuremath{\Ptop\bar{\Ptop}\PW}\xspace}
\DeclareDocumentCommand\ttbar{}{\ensuremath{\Ptop\bar{\Ptop}}\xspace}
\DeclareDocumentCommand\qqbar{}{\ensuremath{\Pq\Pqbar}\xspace}
\DeclareDocumentCommand\bbbar{}{\ensuremath{\text{b}\bar{\text{b}}}\xspace}
\DeclareDocumentCommand\ccbar{}{\ensuremath{\text{b}\bar{\text{b}}}\xspace}
\DeclareDocumentCommand\ttX{}{\ensuremath{\Ptop(\bar{\Ptop})\text{X}}\xspace}
\DeclareDocumentCommand\PmW{}{\ensuremath{\text{m}_\text{W}\xspace}}
\DeclareDocumentCommand\PmZ{}{\ensuremath{\text{m}_\text{Z}\xspace}}

\DeclareDocumentCommand\PMuE{}{\ensuremath{\mu_\text{e}}\xspace}
\DeclareDocumentCommand\pT{}{\ensuremath{p_\text{T}}\xspace}
\DeclareDocumentCommand\Peta{}{\ensuremath{\eta}\xspace}
\DeclareDocumentCommand\pTcorr{}{\ensuremath{p_\text{T}^\text{corr}}\xspace}
\DeclareDocumentCommand\HT{}{\ensuremath{\text{H}_\text{T}}\xspace}
\DeclareDocumentCommand\pTVec{}{\ensuremath{\vec{\pT}}\xspace}
\DeclareDocumentCommand\MT{}{\ensuremath{\text{M}_\text{T}}\xspace}
\DeclareDocumentCommand\pTmiss{}{\ensuremath{\pT^\text{miss}}\xspace}
\DeclareDocumentCommand\HTmiss{}{\ensuremath{\text{H}_\text{T}^\text{miss}}\xspace}
\DeclareDocumentCommand\pTmissVec{}{\ensuremath{\vec{\pT}^\text{miss}}\xspace}
\DeclareDocumentCommand\met{}{\ensuremath{{E}_T^\text{miss}}\xspace}

\DeclareDocumentCommand\njets{}{\ensuremath{N_\text{jets}}\xspace}
\DeclareDocumentCommand\nbjets{}{\ensuremath{N_\text{b}}\xspace}

\DeclareDocumentCommand\f{mm}{\ensuremath{#1\mathopen{}\left(#2\right)}}
\DeclareDocumentCommand\amcatnlo{}{\mbox{\textsc{mg5\_amc@nlo}}\xspace}
\DeclareDocumentCommand\powheg{}{\mbox{\textsc{powheg}}\xspace}
\DeclareDocumentCommand\mcfm{}{\mbox{\textsc{mcfm}}\xspace}
\DeclareDocumentCommand\madgraph{}{\mbox{\textsc{Madgraph}}\xspace}
\DeclareDocumentCommand\pythia{}{\mbox{\textsc{Pythia}}\xspace}
\DeclareDocumentCommand\PYTHIA{}{\mbox{\textsc{Pythia}}\xspace}
\DeclareDocumentCommand\geant{}{\mbox{\textsc{Geant}4}\xspace}
\DeclareDocumentCommand\madspin{}{\mbox{\textsc{Madspin}}}
\DeclareDocumentCommand\eightTeV{}{\SI{8}{TeV}\xspace}
\DeclareDocumentCommand\thirteenTeV{}{\SI{13}{TeV}\xspace}

\DeclareRobustCommand{\eg}{e.g.\@\xspace}
\DeclareRobustCommand{\ie}{i.e.\@\xspace}

\DeclareDocumentCommand\TeV{}{\ensuremath{\text{TeV}}\xspace}

\DeclareDocumentCommand\cB{}{\ensuremath{\bar{c}_{\text{B}}}\xspace}
\DeclareDocumentCommand\cH{}{\ensuremath{\bar{c}_{\text{H}}}\xspace}
\DeclareDocumentCommand\cHB{}{\ensuremath{\bar{c}_{\text{HB}}}\xspace}
\DeclareDocumentCommand\cHu{}{\ensuremath{\bar{c}_{\text{Hu}}}\xspace}
\DeclareDocumentCommand\cHud{}{\ensuremath{\bar{c}_{\text{Hud}}}\xspace}
\DeclareDocumentCommand\cHQ{}{\ensuremath{\bar{c}_{\text{HQ}}}\xspace}
\DeclareDocumentCommand\cpHQ{}{\ensuremath{\bar{c}^{\prime}_{\text{HQ}}}\xspace}
\DeclareDocumentCommand\cthreeG{}{\ensuremath{\bar{c}_{\text{3G}}}\xspace}
\DeclareDocumentCommand\cthreeW{}{\ensuremath{\bar{c}_{\text{3W}}}\xspace}
\DeclareDocumentCommand\ctwoG{}{\ensuremath{\bar{c}_{\text{2G}}}\xspace}
\DeclareDocumentCommand\cu{}{\ensuremath{\bar{c}_\text{u}}\xspace}
\DeclareDocumentCommand\cuB{}{\ensuremath{\bar{c}_{\text{uB}}}\xspace}
\DeclareDocumentCommand\cuG{}{\ensuremath{\bar{c}_{\text{uG}}}\xspace}
\DeclareDocumentCommand\cuW{}{\ensuremath{\bar{c}_{\text{uW}}}\xspace}
\DeclareDocumentCommand\tcA{}{\ensuremath{\widetilde{c}_{\text{A}}}\xspace}
\DeclareDocumentCommand\tcHW{}{\ensuremath{\widetilde{c}_{\text{HW}}}\xspace}
\DeclareDocumentCommand\tcthreeG{}{\ensuremath{\widetilde{c}_{\text{3G}}}\xspace}
\DeclareDocumentCommand\doublehat{m}{\ensuremath{\smash{\hat{\hat{#1}}}}}

\DeclareDocumentCommand\sigmaSMNP{}{\ensuremath{\sigma_\text{NP+SM}}\xspace}
\DeclareDocumentCommand\sigmaSM{}{\ensuremath{\sigma_\text{SM}}\xspace}

\makeatletter
\DeclareRobustCommand{\etc}{%
    \@ifnextchar{.}%
        {etc}%
        {etc.\@\xspace}%
}
\makeatother


\setdefaultlanguage[variant=us]{english}

\setmainfont{Libertinus Serif}
\setmathfont{Libertinus Math}

\frenchspacing

\xapptocmd{\bibsetup}{\singlespacing}{}{}

\addto\captionsenglish{%
  \renewcommand{\abstractname}{Abstract}
  \renewcommand{\dedicationname}{\mbox{}}
  \renewcommand{\prefacename}{Preface}
  \renewcommand{\acknowledgename}{Acknowledgments}
  \renewcommand{\symbolsname}{Symbols}
  \renewcommand{\tablename}{Table}
  \renewcommand{\figurename}{Figure}
  \renewcommand{\partname}{Part}
  \renewcommand{\chaptername}{Chapter}
  \renewcommand{\appendixname}{Appendix}
  \renewcommand{\contentsname}{Contents}
  \renewcommand{\listfigurename}{Figures}
  \renewcommand{\listtablename}{Tables}
  \renewcommand{\bibname}{Bibliography}
  \renewcommand{\indexname}{Index}
}

\makeatletter
\g@addto@macro\@floatboxreset\centering
\makeatother


\title{Effective field theory interpretation for measurements of top quark
pair-production in association with a W or Z boson}
\author{Anna Elizabeth Woodard}
\copyrightlicense{\doclicenseText \\ \doclicenseIcon}
\work{Dissertation}
\degaward{Doctor of Philosophy}
\advisor{Kevin Lannon}
\department{Physics}

\begin{document}

\frontmatter
\maketitle
\makecopyright

\begin{abstract}
  Using effective field theory, the effects of new particles or interactions can
  be captured in a model-independent way by supplementing the standard model
  Lagrangian with higher-dimensional operators. A measurement of the cross
  section for top quarks produced in association with a W or Z boson, using
  \SI{19.5}{\per\femto\barn} of proton-proton collisions with a center-of-mass energy of
  \eightTeV, collected by the CMS experiment at the LHC, is extended within this
  framework to set constraints on the Wilson coefficients of five dimension-six
  operators. An additional measurement of the same processes using
  \SI{35.9}{\per\femto\barn} of proton-proton collisions with a center-of-mass energy of
  \thirteenTeV collected by the CMS experiment is used to perform a more
  sophisticated study of eight dimension-six operators and present bounds on
  their Wilson coefficients.
\end{abstract}

\begin{dedication}
  Dedicated to Gilbert,
  despite a talk which began frantically after he sat
  on my keyboard and deleted my slides
\end{dedication}

\tableofcontents
\listoffigures
\listoftables

\begin{acknowledge}
I first thank the Large Hadron Collider accelerator team for their tireless work
building and running this spectacular machine. I would also like to thank all of
the members of the Compact Muon Solenoid collaboration. Without the dedication
of these two groups of people, this dissertation would not have been possible.

At Notre Dame, I have had the good fortune of working with and learning from
many talented professors. Special thanks are due to my advisor Kevin Lannon. He
has provided me with guidance, encouragement, and many opportunities to pursue
interesting research. He has afforded me freedom to work on side projects which
have significantly enriched my time in graduate school. I am grateful for his
unwavering support, especially during a period when circumstances required I
take some time away from school. I am also thankful to Kevin's postdoc Jason
Slaunwhite and to my fellow student Andrew Brinkerhoff. Jason and Andrew were
critical to my day-to-day training as a particle physicist. Notre Dame faculty
members Michael Hildreth, Randy Ruchti, Mitch Wayne, and Colin Jessop deserve
thanks for creating a great atmosphere for doing particle physics research at
Notre Dame.

Before graduate school, there were a number of professors at Florida State that
encouraged me. I would like to thank my undergraduate advisor Volker Crede in
particular, who gave me my first opportunity to participate in physics research,
and helped me get started down this path. He took a chance on me, despite having
me in his introductory physics class, which was before I learned how to study.

My time at CERN and in South Bend have been enormously enriched by the friends I
have made there. I would like to thank Matthias Wolf especially. We built
Lobster together, a software tool which has been one of the most rewarding side
projects I have had the opportunity to work on. I thank him for being such a
great friend throughout the years. I would also like to thank Ted Kolberg, Jamie
Antonelli, Sean Lynch, Rachel Yohay, Dave and Kat Morse, Nil Valls, John Wood,
Nathan Kellams, Michael Planer, Douglas Berry, Tessa Pearson, Allison Reinsvold,
Fanbo Meng, Sarah Boutle, Chris Neu, Justin Griffiths, Nabarun Dev, Mayukh Raj
Gangopadhyay, Charlie Mueller, Wuming Luo, Geoffrey Smith, Andrew Wightman,
Wenzhao Li, Jeff Kolb, and countless others.

I owe a great debt to the many theorists who have helped me along the way. Thank
you for providing guidance and patiently answering my questions. Special thanks
go to Adam Martin, Fatimah Elahi, Landon Lehman, Ayan Paul, Joe Bramante, Brian
Ostdiek, Fabio Maltoni and Eleni Vryonidou.

My analysis depended on Lobster, which could not have been developed without the
tools and support provided by Douglas Thain's Cooperative Computing Laboratory
at Notre Dame. I am grateful to Professor Thain for his insight and guidance in
computing matters. I would also like to thank Benjamin Tovar, Patrick Donnelly,
Peter Ivie, Haiyan Meng, and the rest of the CCL team. I am also thankful to
Kevin's postdoc Kenyi Paolo Hurtado Anampa for his friendship and computing
help. Likewise, my work would not have been possible without Serguei Federov,
Paul Brenner, Scott Hampton, and the rest of the team at Notre Dame's Center for
Research Computing. Thanks for putting up with me. Sorry about that time I
accidentally hammered the cluster with misconfigured jobs writing two hundred
gigabyte log files. I would also like to thank the CMS CRAB3 team and the HLT
team. I am forever in the debt of the unnamed masses at Stack Overflow: this
dissertation would have taken several more years without you.

I am grateful to the 13 TeV ttV team for taking me in: Didar Dobur, Illia
Khvastunov, Mirena Paneva, and Deniz Poyraz.

I could never have written this dissertation without the love and support of my
friends and family: my parents, Margaret and Daniel Woodard (who also deserves
thanks for proofreading this dissertation); my uncle Michael Barnes; my brothers
and many other cousins, aunts, and uncles; and Nora Jacobsen Ben Hammed, Mallory
Smith, and Glenn Anderson. Finally, I would like to thank my best friend Amy
Doran and my husband Orin Harris for their love and support; and to thank Orin
for his patience, and Amy for her impatience.

\end{acknowledge}

\mainmatter

\include{chapters/introduction}
\include{chapters/theory}
\include{chapters/apparatus}
\include{chapters/objects}
\include{chapters/8-TeV}
\include{chapters/13-TeV}
\include{chapters/eft-analyses}
\include{chapters/conclusions}
\appendix
\include{chapters/reproducibility}
\include{chapters/2d-scans}

\backmatter

% \bibliographystyle{nddiss2e}
% \bibliography{physics}
\nocite{Ellis:2016jkw}
\singlespacing
\printbibliography[heading=bibintoc]

\end{document}
